\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
adding short title and page number

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{\tname: A Database of Reproducible Bugs in Deep
  Learning Libraries to Enable Systematic Evaluation of Testing
  Techniques}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

>>>>

%% The "title" command has an optional parameter, allowing the author
%% to define a "short title" to be used in page headers.

\newcommand{\myshort}{\tname~: A Database of Reproducible Bugs in
  Deep Learning Libraries}

\title[\myshort{}]{\myshort{} to Enable Systematic Evaluation of
  Testing Techniques}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
%% add page numbers
\pagestyle{plain}
